### 2019-02-19 README.Rmd
Description of datasets (from raw to analysis)

>>>>

## Structure of the project repository

### Raw data

Raw datas are spreadsheets (xls, csv, etc...) shapefiles and others cartographic
data and reports (of the AFB, ONEMA, etc). The raw datas come together with `R`
scripts which describe cleaning procedures. The cleaning procedures end by
saving datasets used for data analysis.

It is located in `data-raw`.

### Data for analysis

The clean datasets live in `data` directory and stored in `rda` compressed format.
Once the package is loaded, they can be call as easily as `load(objet_name)`.

```{r}
devtools::load_all()
data(metaweb_analysis)
names(metaweb_analysis)
```
The cleaned and filtered objects used for data analysis are named with the suffix `_analysis`.

### Analysis of data

The analysis of data lives in the directory named `analysis`.

This folder contains scripts in which various metrics are computed for two
different aspects that have been more or less arbitrary separated.

#### Community data

The community data lives in the `community_analysis` and contains the following
data:

- species abondances
- species biomass
- species richness

The following metrics are summarised by station in `community_metrics`:

- mean and cv of species richness
- mean and cv of species biomass 
- temporal beta-diversity

#### Network data

The network data lives in the `network_analysis` and contains the following
metrics:

- connectance
- number of nodes
- modularity and modules 
- nestedness 
- trophic length

The following metrics are summarised by station:

- mean and cv of all the above indices
